Solutions to Integer Programming from Quantum Annealing

### 2020-05-09 paper/main.tex
very rough first draft. need to write methods also

\subsection{Finding the Dominating Set with a Quantum Annealer}

\begin{figure}[b]
	\centering
		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
	\label{fig:linear}
\end{figure}

@@

{\color{red} Should we talk about exponential damping here too? as a competing effect.}

{\color{blue} (I tried to write something here...) Intuitively, we want the system to explore larger state space to increase the probability for the system to reach the final ground state. That is, we want the system to have ergodicity to avoid MBL. On the other hand, decoherence in the hardware leads to the loss of quantum information. It is desirable to minimize the effect of relaxation. The interplay between these two competing effects causing the complications in the results of annealing schedule offsets. Insights can be obtained by looking at the mutual information $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition A and partition B of the total system. $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.
(Should we talk about mutual information here? or in the latter MBL part? )}

@@

Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits.

@@

@@

\section{METHODS}
\subsection{Simulation Details}
\subsubsection{The Lindblad Equation}
Say what the simulator is solving

@@

\subsubsection{Decoherence Time}
Scan over decoherence time

>>>>

\subsection{Finding the Dominating Set with a Quantum Annealer}
\label{sec:discussion:qa}
\begin{figure}[b]
	\centering
		\includegraphics[width=0.5\columnwidth]{./figures/linear_crop.pdf}
	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
	\label{fig:linear}
\end{figure}

@@

@@

Finally, we note that due to the inherent variance in performance when using different physical qubits, for each graph, we perform the offset study on the same physical qubits. Additionally, the largest offset ranges sampled are at the limits of the hardware capabilities of the DWave annealer.

We observe from Fig.~\ref{fig:dwave_offset} that advancing qubits subject to \textit{larger} final external magnetic fields yields approximately an order of magnitude improvement over the baseline results at the largest offset range. In contrast advancing qubits with weaker magnetic fields consistently hurts the performance of the annealer. This result is surprising in light of the expectation from many-body localization. We provide an explanation of this surprising result by simulating the annealing process of the annealer which are discussed in the following sections.

@@

In order to understand the effects of annealing offsets, we simulate the annealing process on 5 qubits for a $G(2)$ graph embedded in chimera topography. In order to shorten the simulation time, we resample the DWave with a total annealing time of 1 $\mu s$. The resulting ground state probability as a function of offset measured over 200,000 observations is shown in Fig.~\ref{fig:dwave1us} (Top).

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./figures/dwave1us.pdf}
	\includegraphics[width=\columnwidth]{./figures/sim_deco.pdf}
	\includegraphics[width=\columnwidth]{./figures/sim_nodeco.pdf}
	\caption{ (Top) The probability of finding the MDS for $G(2)$ from DWave. The machine parameters are identical to Sec.~\ref{sec:discussion:qa} with the exception of shortening the total annealing time to 1 $\mu s$ to accommodate reasonable simulation times. (Middle) Result from simulation with decoherence and (Bottom) simulation without decoherence. In both simulations, at +10\% offset, the probability of finding the ground state vanishes. The red simulation points are not present in the DWave result.}
	\label{fig:dwave1us}
\end{figure}

For the simulation, the QUBO is obtained from the output of the DWave such that the same embedding is used. The time-dependence is obtained by solving the Lindblad equation subject to the DWave annealing schedule with offsets allowing us to incorporate a decoherence model in our simulation. The details of the Lindbladian are given in Sec.~\ref{sec:methods:lindblad}. Following Ref.~\cite{}, we fix the temperature of the simulation to 15 milliKelvins to reflect the reported operating temperature of the DWave. Due to the small size of the problem, the minimum gap to the second excited state (first non-degenerate state) of the time-dependent Hamiltonian is approximately 2 Kelvins as shown in Fig.~\ref{fig:spectrum}. As a result, the DWave operates at effectively zero-temperature for this example problem.

We then set an effective $T_1$ coherence time to 20 $ns$ in order to match the DWave probability of finding the MDS of $G(2)$ at approximately 86\%. A detailed study of $T_1$ is given in Sec.~\ref{sec:methods:deco}. We emphasize that the effective coherence time is much longer than the single qubit coherence time of 0.5 $ns$ reported by DWave, while still being orders of magnitude shorter than the total anneal time. The simulation and the experiment however, both are able to recover the ground state with high probability regardless, and exemplifies the robustness of quantum annealing.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{./figures/spectrum.pdf}
	\includegraphics[width=\columnwidth]{./figures/spectrum_offset.pdf}
	\caption{The energy spectrum of the first 5 states of the time-dependent Hamiltonian (Top) without annealing offsets and (Bottom) -10\% annealing offset. The spectrum in dimensionless units at the end of the anneal is an integer spectrum and correspond to the number of vertices in the dominating set. For $G(2)$, the MDS has 1 vertex. Annealing offsets lift the ground-state degeneracy.}
	\label{fig:spectrum}
\end{figure}

The probability of finding the MDS from the simulation with and without decoherence are given in Fig.~\ref{fig:dwave_offset} (Middle) and (Bottom). We observe that with decoherence, the simulation captures the rough features of the experiment, including a steady improvement for negative offsets, and similar non-linear behavior at positive offsets. Additionally, the range of probabilities in the simulation non-trivially match the range observed in experiment. In contrast, simulations without decoherence exemplify the opposite behavior with respect to offsets, in line with expectation from many-body localization. Therefore, the simulation provides evidence in relating the improvement seen on the DWave to the effects of decoherence rather than many-body localization, while for idealized annealing, the effects of many-body localization become important.

In both simulations, the system experience a relatively large jump in probability, at -10\% and +30\% respectively. For the simulation with decoherence, this behavior is inconsistent with experiment.  {\color{red} eh.. guess a reason?} Additionally, both simulations experience vanishing probability at +10\% offset. This behavior is expected to happen eventually in experiment as well when the two sets of qubits become too aggressively staggered and effectively decouple. The simulation however, incorrectly predicts when the decoupling happens.

@@

We provide further evidence of the competing effects between decoherence and many-body localization in this section.

Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state. That is, we want the system to have ergodicity in order to avoid MBL. On the other hand, decoherence in the hardware leads to the loss of quantum information. It is therefore desirable to minimize the effect of relaxation. The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information. The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system. $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.

\begin{figure*}
	\centering
	\includegraphics[width=\columnwidth]{./figures/full_prob_deco.pdf}
	\includegraphics[width=\columnwidth]{./figures/mutual_info_deco.pdf}
	\includegraphics[width=\columnwidth]{./figures/full_prob_nodeco.pdf}
	\includegraphics[width=\columnwidth]{./figures/mutual_info_nodeco.pdf}
	\caption{(Left) The time-dependent probability of resolving the ground state and (Right) the corresponding mutual information. (Top) Simulation with decoherence included and (Bottom) without decoherence.}
	\label{fig:prob_mi}
\end{figure*}

From Fig.~\ref{fig:prob_mi} we observe that when the anneal schedule is modified to delay stronger external magnetic fields, the phase transition is delayed, yielding larger mutual information, and in turn probes a larger state space. This observation is independent of the effects of decoherence, and only relies on delaying the phase transition later in the annealing process. It then follows that the effects of decoherence is in competition with delocalization because the system is required to exhibit its quantum mechanical nature for longer. In contrast, if the phase transition is advanced, effects of decoherence are more suppressed since the system freezes to its classical solution earlier in the annealing process and become unaffected by decoherence. This phenomena is demonstrated by the left panels in Fig.~\ref{fig:prob_mi} where in the case of decoherence, the schedule which delays the phase transition consistently underperforms the (bahhh help me word this. top one the red is always below blue, the bottom one, the red crosses the blue after the phase transition).

Things to do:

Compute dwave mutual information

Study ground state degeneracy by plotting distribution of states.

\section{METHODS}
\subsection{Simulation Details}
\subsubsection{The Lindblad Equation}
\label{sec:methods:lindblad}
Say what the simulator is solving

@@

\subsubsection{Decoherence Time}
\label{sec:methods:deco}
Scan over decoherence time
